Exploring mathematical objects from custom-tailored mathematical universes

### 2020-01-19 paper-filmat.tex
References to the automatic continuity

\bigskip
\dotparagraph{``Any function~$\RR \to \RR$ is continuous.''}\label{sect:eff-continuous}
In the standard topos, this statement is plainly false, with the signum and Heaviside functions
being prominent counterexamples. In the \effective topos, this statement is
true. A rigorous proof is not entirely straightforward~\cite{XXX}, but an intuitive
explanation is as follows.

>>>>

\bigskip
\dotparagraph{``Any function~$\RR \to \RR$ is continuous.''}\label{sect:eff-continuous}
In the standard topos, this statement is plainly false, with the signum and Heaviside functions
being prominent counterexamples. In the \effective topos, this statement is
true and independently due to
Kreisel--Lacombe--Shoenfield~\cite{kreisel-lacombe-shoenfield:cont} and
Ceĭtin~\cite{ceitin:cont}. A rigorous proof is not entirely
straightforward (a textbook reference
is~\cite[Thm.~9.2.1]{longley-normann:higher-order-computability}), but an intuitive
explanation is as follows.
